\documentclass[11pt,a4paper]{article}

% Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{tcolorbox}
\usepackage{tikz}
\usepackage{fontawesome5}
\usepackage{lmodern}
\usepackage{tikz}
\usepackage{titlesec}

% Page geometry
\geometry{
    left=2cm,
    right=2cm,
    top=2.5cm,
    bottom=2.5cm
}

% Color definitions
\definecolor{primaryBlue}{RGB}{33, 150, 243}
\definecolor{accentTeal}{RGB}{0, 188, 212}
\definecolor{darkNavy}{RGB}{25, 42, 86}
\definecolor{lightGray}{RGB}{250, 250, 250}
\definecolor{mediumGray}{RGB}{189, 189, 189}
\definecolor{successGreen}{RGB}{76, 175, 80}
\definecolor{warningOrange}{RGB}{255, 152, 0}

% Title formatting with modern design
\titleformat{\section}
  {\color{white}\LARGE\bfseries\sffamily}
  {\tikz[baseline=(char.base)]{\node[shape=circle,fill=white,text=primaryBlue,minimum size=1.2cm,font=\Large\bfseries] (char) {\thesection};}}{0.5em}{}[
  \vspace{-1.2em}
  \begin{tikzpicture}[remember picture, overlay]
    \fill[primaryBlue] (0,0) rectangle (\textwidth, 0.8cm);
    \node[anchor=west, text=white] at (1.5cm, 0.4cm) {\LARGE\bfseries\sffamily};
  \end{tikzpicture}
  \vspace{0.3cm}
]

\titleformat{\subsection}
  {\color{darkNavy}\large\bfseries\sffamily}
  {\tikz[baseline=(char.base)]{\node[shape=rectangle,rounded corners,fill=accentTeal!20,text=accentTeal,inner sep=4pt,minimum width=1.5cm,font=\normalsize\bfseries] (char) {\thesubsection};}}{0.5em}{}

% Hyperref setup
\hypersetup{
    colorlinks=true,
    linkcolor=primaryBlue,
    urlcolor=primaryBlue,
    pdftitle={SavoyConnect Features - Database Reference},
    pdfauthor={Rifaf Rahman},
    pdfsubject={Feature Documentation for Database Design}
}

% Header and footer with modern styling
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\color{primaryBlue}\sffamily\textbf{SAVOYCONNECT} \color{mediumGray}| \color{darkNavy}Features Reference}
\fancyhead[R]{\tikz{\node[circle,fill=primaryBlue,text=white,minimum size=0.7cm,font=\small\bfseries]{\thepage};}}
\fancyfoot[L]{\color{mediumGray}\small\sffamily Database Design Reference}
\fancyfoot[R]{\color{mediumGray}\small\sffamily November 2025}
\renewcommand{\headrulewidth}{1.5pt}
\renewcommand{\headrule}{\hbox to\headwidth{\color{primaryBlue}\leaders\hrule height \headrulewidth\hfill}}
\renewcommand{\footrulewidth}{0.5pt}
\renewcommand{\footrule}{\hbox to\headwidth{\color{mediumGray}\leaders\hrule height \footrulewidth\hfill}}

\begin{document}

% Modern Title Page
\begin{titlepage}
    % Top colored header
    \begin{tikzpicture}[remember picture,overlay]
        \fill[primaryBlue] (current page.north west) rectangle ([yshift=-6cm]current page.north east);
        \fill[accentTeal] ([yshift=-6cm]current page.north west) rectangle ([yshift=-6.3cm]current page.north east);
    \end{tikzpicture}
    
    \vspace*{1.5cm}
    
    % Title
    {\color{white}\sffamily
    {\Huge\bfseries SAVOYCONNECT}\\[0.5cm]
    {\LARGE Features Reference}\\[0.2cm]
    {\large Database Design Documentation}
    }
    
    \vspace{3cm}
    
    % Info box
    \begin{tcolorbox}[
        colback=white,
        colframe=primaryBlue,
        boxrule=2pt,
        arc=4mm,
        width=0.75\textwidth,
        left=10pt,
        right=10pt,
        top=15pt,
        bottom=15pt
    ]
    \sffamily
    \begin{tabular}{@{}ll}
        \textcolor{primaryBlue}{\faUser\ \textbf{Prepared by:}} & Rifaf Rahman \\[0.4cm]
        \textcolor{primaryBlue}{\faBriefcase\ \textbf{Role:}} & Intern, Data Limited \\[0.4cm]
        \textcolor{primaryBlue}{\faCalendar\ \textbf{Date:}} & November 2025 \\[0.4cm]
        \textcolor{primaryBlue}{\faDatabase\ \textbf{Purpose:}} & Database Schema Design \\[0.4cm]
        \textcolor{primaryBlue}{\faList\ \textbf{Total Features:}} & 29 Features across 10 Categories \\
    \end{tabular}
    \end{tcolorbox}
    
    \vfill
    
 
    
\end{titlepage}

\tableofcontents
\newpage

% Main content
\section{Core Commerce Features}

\subsection{Ordering Flow}
Order ice cream by pieces (boxes) or liters with real-time price calculation, delivery fee threshold, minimum order validation, and structured delivery form.

\subsection{Delivery Tracking}
Real-time order tracking with live status updates (Order Confirmed, Preparing, Out for Delivery, Delivered), delivery personnel details, estimated arrival time, live GPS map, and push notifications for status changes.

\subsection{Payment Methods \& Preferences}
Save and manage multiple payment methods (card, mobile wallet, cash on delivery) with default selection and payment preferences.

\subsection{Customer Care \& Help Center}
Customer support access with FAQs, contact forms, chat support, and company information (About Us, Terms, Privacy Policy).

\section{User Engagement \& Social Features}

\subsection{Flavor Ratings \& Reviews}
Users can rate flavors (1-5 stars) and write text reviews with optional photos. Reviews can be reported for moderation.

\subsection{Store Reviews}
Location-specific reviews for physical stores, depots, and outlets with ratings and feedback on service quality.

\subsection{Community Feed}
Social feed where users post photos, share flavor reviews, celebrate challenge completions, and interact through likes, comments, and shares. Includes hashtag support and moderation.

\section{Content \& Discovery}

\subsection{Recipe Discovery}
Browse recipes with categories, filters, detailed ingredients, step-by-step instructions, photos, and links to products used.

\subsection{Search \& History}
Search for recipes with search history tracking and recently viewed recipes.

\subsection{News \& Campaign Feed}
In-app news feed for flavor launches, seasonal offers, CSR updates, and promotional campaigns.

\section{Loyalty \& Rewards}

\subsection{Wallet \& Loyalty (IceCoins)}
Virtual currency wallet showing balance, transaction history, ways to earn coins (purchases, challenges, referrals), and redemption options for rewards.

\subsection{Challenges \& Missions}
Goal-based challenges with progress tracking and IceCoins rewards. Examples: "Try 5 new flavors", "Share 3 photos", "Use reusable cup 5 times".

\subsection{Referral Rewards}
Invite friends via referral link/code with rewards for both referrer and referee. Supports tiered bonuses.

\subsection{Promotions \& Ads Center}
Centralized promotional banners, special offers, and campaign announcements with deep links to features, products, or offers.

\section{Location \& Inventory}

\subsection{Nearby Availability Finder}
Search for flavors and see real-time stock availability at nearby locations (stores, depots, freezers) with substitute suggestions when out of stock.

\subsection{Map View \& Directions}
Interactive map showing nearby Savoy locations with filters (open now, services available) and one-tap navigation to selected location.

\subsection{Stock Notification System}
"Notify me" alerts when out-of-stock flavors become available at nearby locations. Notifications via push, email, or in-app.

\section{Personalization \& AI}

\subsection{AI Flavor Recommendation Engine}
Personalized flavor suggestions based on purchase history, preferences, seasonal trends, weather, and user behavior.

\subsection{Digital Ice Cream Passport}
Track flavors tried with visual progress, earn badges ("Chocolate Lover", "Explorer"), and view flavor journey timeline.

\subsection{Make-Your-Own-Box}
Create custom gift boxes by selecting individual flavors per slot, choose packaging, add gift message, recipient details, and schedule delivery or pickup.

\subsection{Birthday Gift Feature}
Automatic birthday detection with special offers, time-bound coupons, or personalized greetings sent to users.

\section{Health \& Sustainability}

\subsection{Health \& Nutrition Hub}
Health profile with weight, height, BMI calculator, dietary preferences, allergen alerts, daily calorie goal tracking, nutrition comparison between flavors, and "Perfect Match" recommendations.

\subsection{Eco Meter \& Sustainability Tracker}
Track personal environmental impact per purchase (plastic saved, carbon offset, trees planted) with badges, levels (Eco Beginner to Eco Hero), and cumulative progress.

\section{Gamification \& Engagement}

\subsection{Games Hub}
Collection of online games, offline games, AR location-based games, and city-wise competitions. Supports game subscriptions purchasable with IceCoins.

\subsection{Leaderboards}
Ranking system showing top users by IceCoins earned, challenges completed, or game scores with period filters (weekly, monthly, all-time).

\section{Trust \& Transparency}

\subsection{Barcode/QR Scan}
Scan product QR codes or barcodes to verify authenticity, view detailed ingredients/allergens, access active promotions, and earn bonus IceCoins.

\subsection{In-App Feedback \& CSAT}
Feedback submission form with category selection (Bug, Suggestion, Compliment, Other), satisfaction rating, free-text comments, and optional screenshot attachment.

\section{Infrastructure \& Platform}

\subsection{Accounts \& Authentication}
User registration with email/password, profile information (name, email, phone, DOB, gender, address, city), login, password reset, and acceptance of Terms \& Privacy Policy.

\subsection{Notifications \& Toasts}
System notifications for order updates, delivery status, promotional alerts, challenge completions, wallet transactions, and in-app toast messages for user actions.

\vspace{1.5cm}



\end{document}
